### 2017-10-02 Gruba/03-fe.tex
v3.0
v3.0

If $sim(b, t)$ satisfies a certain threshold, topic $t$ is labeled to blog $b$; 
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon, the explicit interests of $u$ is returned, in the form of interest feature (see Definition \ref{def:inte}).

@@

\textit{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA \refe{} to result the word weight distribution of blog $b$. 
Unlike TF-IDF \refe{}, Twitter-LDA \refe{} first trains the overall blogs, allocating each blog with a \textit{tag}. 
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$.
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textit{Step 6}.

@@

Among the $n$ dimensions of $S(u,\ L)$, those with top $x$ similarity values are selected to label the implicit interests of user $u$, which results an $x$ dimensional vector $P_f$ as described in Definition \ref{def:inte}.
Similarly, interest features of all users are returned.

>>>>

If $sim(b, t)$ satisfies a certain threshold (3 by default) , topic $t$ is labeled to blog $b$; 
the user $u$ is then discovered having an explicit interest (topic) $t$.
Thus, by looking into the similarity of $b$ against all topics in lexicon, the explicit interests of $u$ is returned, in the form of interest feature (see Definition \ref{def:inte}).

@@

\textit{Step 4:} Similarly, another metric \textit{Twitter-LDA weight} $W_w$ is obtained, i.e., using Twitter-LDA \refe{} to result the word weight distribution of blog $b$. 
Unlike TF-IDF \refe{}, Twitter-LDA \refe{} first trains the overall blogs, allocating each blog with a \textit{tag}. 
%
The structure of \textit{tag} is as follows:
\begin{equation}
\label{eq:tw-tag}
W_t = \{(w'_i, p'_i)\}
\end{equation}
where $w'_i$ refers to a word in \textit{tag} $W_t$, and $p'_i$ is the probability that $w'_i$ appears in blogs with the said \textit{tag}, with $\sum_{\substack{i}} p'_i = 1$ ($|W_t|\ =\ 30$ by default).
%
Subsequently, $W_t$ are leveraged to conclude $W_w$, i.e., $W_w\ =\ W_t$ , which shares the format with that of $W_f$.
Go to \textit{Step 6}.

@@

Among the $n$ dimensions of $S(u,\ L)$, those with top $x$ (3 in \sys{}) similarity values are selected to label the implicit interests of user $u$, which results an $x$ dimensional vector $P_f$ as described in Definition \ref{def:inte}.
Similarly, interest features of all users are returned.

### 2017-10-02 Gruba/06-perf.tex
v3.0
v3.0

\section{\textcolor{red}{Performance Evaluation}}
\label{sec:perf}

>>>>

\section{Performance Evaluation}
\label{sec:perf}

\subsection{Experimental Setting}

Experiments were run on a machine with two Intel Xeon E5C2630 2.4GHz CPUs and 64 GB of Memory, running 64 bit Windows 7 professional system.

We have employed a real-world dataset Sina \refe{} that consists of 24 million blogs that are associated with 43.5K users.

With respect to the parameters of \sys{}, we use the default values as mentioned in previous sections.
Particularly, in Feature Extractor, for practical reason, we employed a smaller testing dataset to obtain the proper value of $\alpha$ for extracting \textit{Interest Feature}; 
in User Cluster, we studied the clustering solutions with the minimum/maximum number of clusters 2 and 10;
in Behavior Modeler, a user's recent 30 days blogs are used for short-term interest analysis and popular words of the latest 24 hours are returned by Ring \refe{} as the Big Thing keyword.

\subsection{Result and Analysis}
Next, we shall report the performance of \sys{} over each component.

\textbf{Feature Extractor}
%
Fig.\ \ref{fig:fe} shows the testing results of using various $\alpha$ values. 
Apparently, \sys{} results the optimal results when $\alpha$ is 0.7, upon which the interest feature extracting is performed for the overall dataset with 43.5K users and 24 million blogs.

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{figures/Interests}
\caption{Testing Results with Various $\alpha$ \tbc{}}
\label{fig:fe}
\end{figure}

\textbf{User Clusterer}
%
Fig.\ \ref{fig:uc} depicts the Silhouette Coefficient Values of multiple clustering solutions, with the cluster number from 2 to 10.
Specially, we used different testing datasets, with \textit{Data} containing the overall 43.5K users and \textit{Data1,...,5} contains 10K randomly selected users each.
Except for \textit{Data1}, solutions with 4 clusters sweep.

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{figures/clustering}
\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets \tbc{}}
\label{fig:uc}
\end{figure}

\textbf{Behavior Modeler}
%
Fig.\ \ref{fig:10} shows the performance of \sys{} against state of the art approach LRC-BQ \refe{}.
We compare the metrics of precision, recall, as well as $F_1$ score.
LRC-BQ \refe{} does not deal with user grouping.
Hence, we not only study the modeling effect per group (i.e., ``Group-One/Two/Three/Four'' with user clustering), but also examine \sys{} versus LRC-BQ \refe{} in the case that all users are in mono group (i.e., ``All-Users'').
The results are interesting in that:
\begin{itemize}
	\item With user clustering, \sys{} performs better than LRC-BQ \refe{} in most cases.
	\item For \sys{}, having user clustering is better than the alternative mono group. Ditto for LRC-BQ \refe{}.
\end{itemize}

\begin{figure}
  \centering
  \subfigure[Precision]{
    \label{fig:10-a} 
    \includegraphics[width=0.4\textwidth]{figures/precision.eps}}
  \hspace{1in}
  \subfigure[Recall]{
    \label{fig:10-b} 
    \includegraphics[width=0.4\textwidth]{figures/recall.eps}}
  \hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:10-c} 
    \includegraphics[width=0.4\textwidth]{figures/F-Measure.eps}}
  \caption{Performance of \sys{} Versus LRC-BQ \tbc{}}
  \label{fig:10} 
\end{figure}

Fig.\ \ref{fig:11} explores the performance of \sys{} when using alternative data items for modeling.
By default, \sys{} uses ``UI+II+MI'', i.e., items of users (UI), blogs (MI) and interactions (II).
How about using other combinations of the above item(s)?
As shown in Fig.\ \ref{fig:11}, the default setting wins in most cases.

\begin{figure}
  \centering
  \subfigure[Precision]{
    \label{fig:11-a} 
    \includegraphics[width=0.4\textwidth]{figures/precisionofdifferentfeatures.eps}}
  \hspace{1in}
  \subfigure[Recall]{
    \label{fig:11-b} 
    \includegraphics[width=0.4\textwidth]{figures/recallofdifferentfeatures.eps}}
  \hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:11-c} 
    \includegraphics[width=0.4\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
  \caption{\sys{} Performance of Using Various Data Items for Modeling \tbc{}}
  \label{fig:11}
\end{figure}

### 2017-10-02 Gruba/08-conclu.tex
v3.0
v3.0

\section{\textcolor{red}{Conclusions}}
\label{sec:conclu}

>>>>

\section{Conclusions}
\label{sec:conclu}

In this work, we have presented \sys{}, a system to model users' \retg{} behavior in social media. 
\sys{} departures from related works by grouping users into clusters, during which features of info, behavior and interests are involved. 
Specially, we have studied interest features from various perspectives, such as long-term/recent interests and explicit/implicit interests. 
Last, we provided the performance evaluation of \sys{} by using real-world datasets and comparing against state of the art approaches, showing its benefits.
